### 2014-03-08 src/analysis.Rnw
update

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

@@

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
<<>>=
odata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='original')
rdata <- subset(stats.df, s.element=='project' & strategy=='xpercentperunit' & kind=='randoop')
@
\subsubsection{x\% selection}
\begin{figure*}[t]
<<x.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

@@

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]

>>>>

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected. \\
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

@@

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Analysis of Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator))

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr)[.]', operator)) # We are ignoring ceil here. add rc if needed.
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames

#odata <- subset(o.f(stats.xp), s.element=='project')
#rdata <- subset(r.f(stats.xp), s.element=='project')
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The x\% random selection criteria results.}
\end{table*}

\begin{figure*}[t]
<<x.per.sel,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:sel}
\end{figure*}[t]

% ----------------------------------------------------------------------
<<count>>=
stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))

o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(l|wl)[.]', operator))
colnames(o.stats.sel.loc) <- new.colnames
colnames(r.stats.sel.loc) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.loc, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.loc, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The loc count selection criteria results.}
\end{table*}

% ----------------------------------------------------------------------
<<one>>=
stats.one <- subset(stats.rest, grepl('^o[.]', operator))

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.one, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.one, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\end{table*}

% ----------------------------------------------------------------------

\if 0
% START HERE
\begin{figure*}[t]
<<xx.per.sel,fig.width=5, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
names=odata$s.power
x = (1:nrow(odata))
o.CI.up = as.numeric(odata$mutant.reduction)+as.numeric(odata$sd.reduction)
o.CI.dn = as.numeric(odata$mutant.reduction)-as.numeric(odata$sd.reduction)
r.CI.up = as.numeric(rdata$mutant.reduction)+as.numeric(rdata$sd.reduction)
r.CI.dn = as.numeric(rdata$mutant.reduction)-as.numeric(rdata$sd.reduction)
plot(odata$mutant.reduction~odata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='blue',pch=16)
axis(1, at=x, labels=names)
arrows(x,o.CI.dn,x,o.CI.up,code=3,length=0.2,angle=90,col='blue')
points(rdata$mutant.reduction~rdata$s.power,xaxt='n', cex=1.5,ylim=c(0,100), xlab='Power',ylab='Reduction', main='Project: Mutant Reduction vs Power',col='red',pch=16)
arrows(x,r.CI.dn,x,r.CI.up,code=3,length=0.2,angle=90,col='red')
#legend("bottomleft",paste(names,": S.E=",data$se),ncol=6,text.width=5)
@
\label{fig:sel}
\end{figure*}[t]

@@

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]
%% END HERE
\fi

### 2014-03-08 src/paper.Rnw
update
udpate

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@

>>>>

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitm}{~MATH~}
%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
%\newcommand{\piti}{~INCREMENTS~}
%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
%
\newcommand{\pitnvmc}{NVMC~}
\newcommand{\pitnc}{NC~}
\newcommand{\pitrc}{RC~}
\newcommand{\pitdc}{DC~}
\newcommand{\pitrv}{RV~}
\newcommand{\pitic}{IC~}
\newcommand{\pitcc}{CC~}
\newcommand{\pitemv}{EMV~}
\newcommand{\pitvmc}{VMC~}
\newcommand{\pitm}{M~}
\newcommand{\pitcb}{CB~}
\newcommand{\piti}{I~}
\newcommand{\pitri}{RI~}
\newcommand{\pitrs}{RS~}
\newcommand{\pites}{ES~}
\newcommand{\pitin}{IN~}
% No space variants.
\newcommand{\Pitnvmc}{NVMC}
\newcommand{\Pitnc}{NC}
\newcommand{\Pitrc}{RC}
\newcommand{\Pitdc}{DC}
\newcommand{\Pitrv}{RV}
\newcommand{\Pitic}{IC}
\newcommand{\Pitcc}{CC}
\newcommand{\Pitemv}{EMV}
\newcommand{\Pitvmc}{VMC}
\newcommand{\Pitm}{M}
\newcommand{\Pitcb}{CB}
\newcommand{\Piti}{I}
\newcommand{\Pitri}{RI}
\newcommand{\Pitrs}{RS}
\newcommand{\Pites}{ES}
\newcommand{\Pitin}{IN}

\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@
